Quality Definitions of Qualities

### 2021-10-15 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
Completion of usability quality

\subsection{\notdone{Usability (external, product, process)}} %\notdone \jc{owner}

@@

\begin{mybox}
\subsubsection*{Usability}
The extent to which software can be used by specified users to achieve specified
requirements with effectiveness, efficiency, and satisfaction in a specified
context of use. 
\end{mybox}

@@

\begin{itemize}
  \item The selected definition uses our selected phrase of ``the extent to
  which'' for consistency with the other definitions.
  \item The selected definition is less ambiguous compared
  to~\ref{UsabilityMcCallEtAl1977},~\ref{UsabilityISO9126},~\ref{UsabilityGhezziEtAl2003}
  and ~\ref{UsabilityDesFoundation} because the selected definition talks about
  specified users, goals and context of use.
  \item The proposed definition covers the ``learn, operate, prepare input, and
  interpret output'' from Definition~\ref{UsabilityMcCallEtAl1977} and ``Learnability'', Memorability'' and ``Errors'' from Definition~\ref{UsabilityNielsenNorman} by the more
  abstract phrase ``achieve specified requirements''.
  \item We changed ``the product'' from Definition~\ref{UsabilityISO16982:2002}
  to ``software'', since this document covers software qualities.
  \item We changed ``goals'' from Definition~\ref{UsabilityISO16982:2002} to
  ``requirements'' for the goal of being unambiguous and consistent.
\end{itemize}

>>>>

\subsection{Usability (external, product, process)} %\jc{owner}

@@

\begin{mybox}
\subsubsection*{Usability}
The extent to which a software product, or development process, can be used by
specified users to achieve specified requirements with effectiveness,
efficiency, and satisfaction in a specified context of use. 
\end{mybox}

@@

\begin{itemize}
  \item The selected definition uses our selected phrase of ``the extent to
  which'' for consistency with the other definitions.
  \item The selected definition is less ambiguous compared
  to~\ref{UsabilityMcCallEtAl1977},~\ref{UsabilityISO9126},~\ref{UsabilityGhezziEtAl2003}
  and ~\ref{UsabilityDesFoundation} because the selected definition talks about
  specified users, goals and context of use.
  \item The proposed definition covers the ``learn, operate, prepare input, and
  interpret output'' from Definition~\ref{UsabilityMcCallEtAl1977} and
  ``Learnability'', Memorability'' and ``Errors'' from
  Definition~\ref{UsabilityNielsenNorman} by the more abstract phrase ``achieve
  specified requirements''.
  \item We changed ``the product'' from Definition~\ref{UsabilityISO16982:2002}
  to ``software product or development process'', since this document covers
  software qualities and the quality definition applies to both the product and
  the process.
  \item We changed ``goals'' from Definition~\ref{UsabilityISO16982:2002} to
  ``requirements'' for the goal of being unambiguous and consistent.
  \item Everything from Definition~\ref{UsabilityISO9126} is included in the
  proposed definition because ``understood and learned and used'' are covered by
  effectively and efficiently achieving specified requirements.  The term
  ``liked'' in Definition~\ref{UsabilityISO9126} is covered by user satisfaction
  in the proposed definition.
  \item The user friendliness synonym for usability, as given by
  Definition~\ref{UsabilityGhezziEtAl2003}, is excluded for consistency; we only
  want to introduce one term: usability.
  \item Definition~\ref{UsabilityDesFoundation} is consistent with the selected
  definition, but Definition~\ref{UsabilityDesFoundation} itself is not
  abstract, since it incorporates examples.
\end{itemize}
